Supplementary Information

### 2021-07-26 doc/manuscript/ForestGEO_treerings_SI.Rmd
add missing info to SI fig legend

![`r RW_interactions_all_legend` Shown are modeled response functions at the minimum and maximum and maximum ends of the DBH range. Other terms in the model are held constant at their medians. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver over the analysis period; shading indicates 1 SD.](tables_figures/pre_temp_groups_dbh_interactions_log_core_measurement_dbh.png){ width=90% }

>>>>

![`r RW_interactions_all_legend` Shown are modeled response functions for species at the minimum and maximum and maximum ends of the DBH range. Other terms in the model are held constant at their medians. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver over the analysis period; shading indicates 1 SD. Species are color coded as in Figure 5.](tables_figures/pre_temp_groups_dbh_interactions_log_core_measurement_dbh.png){ width=90% }
